Implicit assumptions and their impact on photometric redshift PDF performance in the context of LSST

### 2018-12-02 paper/tex/analysis.tex
fix mistaken merge deletion

The probability integral transform (PIT) \citep{Polsterer:16} is defined for each individual galaxy as:
\begin{align}
\label{eq:pit}
\mathrm{PIT} &= \int_{-\infty}^{z_{\rm true}}p(z)\, dz \,.
\end{align}
The distribution of PIT values quantifies the behavior of the {\it ensemble} of \pzpdf s, enabling us to evaluate whether the population of \pzpdf s is, on average, accurate.
The PIT value for each galaxy is the Cumulative Distribution Function (CDF) of its \pzpdf\ evaluated at its true redshift.
A catalogue of \pzpdf s that are accurate should have a flat PIT histogram (i.e., the individual PIT values as samples from each CDF should match a Uniform(0,1) distribution if the CDFs are accurate).
Specific deviations from flatness indicate inaccuracy: overly broad \pzpdf s would manifest as underrepresentation of the lowest and highest PIT values, whereas overly narrow \pzpdf s would manifest as over-representation of the lowest and highest PIT values.
High frequency at only $\mathrm{PIT}\approx0$ and $\mathrm{PIT}\approx1$ indicates the presence of catastrophic outliers with highly inaccurate \pzpdf s where the true redshift of a galaxy is outside of the support of its \pzpdf.
\citet{Tanaka:17} use the histogram of PIT values as a diagnostic indicator of overall code performance, while \citet{Freeman:17} independently define the PIT and demonstrate how its individual values may be used both to perform hypothesis testing (via, e.g., the KS, CvM, and AD tests; see below) and to construct quantile-quantile plots.
%\red{We might want to divide this by redshift to get trends, as the overall PIT could be impacted by true n(z).
%For example, a PIT with nontrivial shape could be due to that behavior being uniform as a function of redshift or significant inaccuracy only in a small range of redshifts where $n(z)$ is large and a flat PIT elsewhere.}

>>>>

The probability integral transform (PIT) has been employed recently to evaluate fidelity of posterior distributions \citep[e.~g.~][]{Bordoloi:10,Polsterer:16,Tanaka:17}.  The PIT value is defined for each individual galaxy as:
\begin{align}
\label{eq:pit}
\mathrm{PIT} &= \int_{-\infty}^{z_{\rm true}}p(z)\, dz \,.
\end{align}
The distribution of PIT values quantifies the behavior of the {\it ensemble} of \pzpdf s, enabling us to evaluate whether the population of \pzpdf s is, on average, accurate.
The PIT value for each galaxy is the Cumulative Distribution Function (CDF) of its \pzpdf\ evaluated at its true redshift.
A catalogue of \pzpdf s that are accurate should have a flat PIT histogram (i.e., the individual PIT values as samples from each CDF should match a Uniform(0,1) distribution if the CDFs are accurate).
Specific deviations from flatness indicate inaccuracy: overly broad \pzpdf s would manifest as underrepresentation of the lowest and highest PIT values, whereas overly narrow \pzpdf s would manifest as over-representation of the lowest and highest PIT values.
High frequency at only $\mathrm{PIT}\approx0$ and $\mathrm{PIT}\approx1$ indicates the presence of catastrophic outliers with highly inaccurate \pzpdf s where the true redshift of a galaxy is outside of the support of its \pzpdf.
\citet{Tanaka:17} use the histogram of PIT values as a diagnostic indicator of overall code performance, while \citet{Freeman:17} independently define the PIT and demonstrate how its individual values may be used both to perform hypothesis testing (via, e.g., the KS, CvM, and AD tests; see below) and to construct quantile-quantile plots.
%\red{We might want to divide this by redshift to get trends, as the overall PIT could be impacted by true n(z).
%For example, a PIT with nontrivial shape could be due to that behavior being uniform as a function of redshift or significant inaccuracy only in a small range of redshifts where $n(z)$ is large and a flat PIT elsewhere.}
